### 2024-04-05 doc/15yrsChange.Rmd
renumber figures (code)

biomass_trends = 2 #line plot showing biomass through time for entire plot and each of the 3 focal sections

loss_gain_net = 3 # 4-panel figure showing ∆AGB, loss, and gain for (a) whole plot, (b) deer exclosure, (c) upland, (d) graveyard

mortality_by_genera = 4 # 2-panel figure showing annual biomass mortality by genera for (a) canopy species and (b) understory species

>>>>

loss_gain_net = 2 # 4-panel figure showing ∆AGB, loss, and gain for (a) whole plot, (b) deer exclosure, (c) upland, (d) graveyard

mortality_by_genera = 3 # 2-panel figure showing annual biomass mortality by genera for (a) canopy species and (b) understory species

biomass_trends = 4 #line plot showing biomass through time for entire plot and each of the 3 focal sections
